\documentclass[10pt]{article}

\usepackage{marvosym}
\usepackage{fontspec}
\usepackage{xunicode,xltxtra,url,parskip}
\defaultfontfeatures{Scale=MatchLowercase,Mapping=tex-text}
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{supertabular}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{xstring}
\usepackage{rotating}
\usepackage{ifthen}
\usepackage[xetex,
            unicode,
            pdfencoding=auto,
            pdfinfo={
              Title={malloc47/cv},
              Author={Jarrell Waggoner},
              Subject={Jarrell Waggoner CV},
              Keywords={computer vision, image processing, artificial intelligence, pattern recognition, machine learning, data science, functional programming, web development, Clojure},
              Producer={xelatex},
              Creator{xelatex}
            },
            ]{hyperref}
\usepackage[absolute]{textpos}
\usepackage{enumitem}
\usepackage{tabularx}

\makeatletter
\renewcommand*{\@biblabel}[1]{\hfill[C#1]}
\makeatother

\include{functions}

\begin{document}
\pagestyle{empty}

% \font\fb=''[cmr10]''

\par{\centering {\Huge Jarrell \textsc{Waggoner} }\bigskip\par}

%% \section{Biographical Data}
%%
%% \begin{tabular}{r p{3.5in}}
%%   \textsc{Address:}	& Department of Computer Science and Engineering, University of South Carolina, Columbia, SC 29208 \\
%%   \textsc{Phone:}     & 847-261-4747\\
%%   \textsc{email:}     & \href{mailto:malloc47@gmail.com}{malloc47@gmail.com} \\
%%   \textsc{Website:}	& \href{http://www.malloc47.com}{www.malloc47.com} \\
%%   \textsc{Citizenship:} & United States Citizen \\
%% \end{tabular}


\begin{multicols}{2}
\setlength{\parskip}{0pt}
  \section{Biographical}

\begin{tabularx}{\linewidth}{@{}l X@{}}
  \textsc{Address}     & \small{600 W Chicago Ave. Suite 400} \\
                       & \small{C/O Groupon, Chicago, IL, 60654-2067} \\
  \textsc{Phone}       & \href{http://www.malloc47.com/call-me/}{847-261-4747} \\
  \textsc{email}       & \href{mailto:jarrell.waggoner@gmail.com}{jarrell.waggoner@gmail.com} \\
\end{tabularx}

\vfill
\columnbreak

\section{Online}
\begin{tabularx}{\linewidth}{@{}l X@{}}
  \textsc{Website}     & \href{http://www.malloc47.com}{www.malloc47.com} \\
  \textsc{Twitter}     & \href{https://twitter.com/malloc47}{@malloc47} \\
  \textsc{github}      & \href{http://www.github.com/malloc47}{github.com/malloc47}\\
  \textsc{LinkedIn}    & \href{http://www.linkedin.com/in/malloc47}{linkedin.com/in/malloc47} \\
\end{tabularx}

\end{multicols}

\section{Research Interests}

computer vision, segmentation, contour completion, perceptual
grouping, document image analysis, event recognition, image
processing, artificial intelligence, pattern recognition \& machine
learning, data science, functional programming, Clojure

\section{Education}
\begin{tabularx}{\linewidth}{@{}r X l}
  \textsc{Aug. 2013} & Ph.D. in \textsc{Computer Science \& Engineering} & \textbf{University of South Carolina}\\
  & \small Advisor: Dr. Song \textsc{Wang} & \\%
  & \footnotesize Dissertation: ``Multi-Label Segmentation Propagation for Materials Science Images Incorporating Topology and Interactivity'' & \\[4ex]%
  \textsc{May} 2009 & Master of Engineering in \textsc{Computer Science} & \textbf{University of South Carolina}\\
  &\normalsize \textsc{GPA}: 3.8/4.0 | \small\emph{magna cum laude} \\[1ex]%
\end{tabularx}

\newcommand{\experience}[4]{
\textsc{#1} & #2 \\
\nopagebreak &\emph{#3}\\
\nopagebreak &\footnotesize{#4} \\
\nopagebreak \multicolumn{2}{c}{} \\ [-1ex]
}

\section{Industry Experience}
\vspace{-1em}
\newcommand{\industry}[4]{
\textsc{#1} & #2 &\emph{#3}\\
&\multicolumn{2}{p{14cm}}{\footnotesize{#4}}\\
\multicolumn{3}{c}{} \\ [-1ex]
}

\begin{longtable}{@{}p{2.2cm}|p{8cm} r}

\industry{2013\textemdash{}Present}%
{Senior Software Engineer}%
{\href{http://www.groupon.com}{Groupon, Inc.}}%%
{Tech Lead of the Supply Intelligence team building internal tools
  and analytics pipelines to optimize Groupon's supply funnel using
  \clojure to develop service-oriented and big data systems.

  \hangindent=1.0em ---~Built a \postgres-backed high-performance
  caching and write management system around \salesforce that hits
  10K req/min

  \hangindent=1.0em ---~Managed a critical business automation of
  the sales lead assignment process that previously required an
  estimated 80 managers to conduct manually; led the effort to
  rearchitect this legacy system from an ad-hoc job scheduling
  platform written in \ruby and \bash to a multi-staged \hadoop
  pipeline written in \clojure

  %% \hangindent=1.0em ---~Operationalized \python within the
  %% organization by spinning up an internal PyPI server; introducing a
  %% pex-driven single-artifact deployment process; creating an
  %% interest group, mailing list, and internal wiki; and standardized
  %% configuration, logging, and resource management

  %% \hangindent=1.0em ---~Developed an end-to-end system and
  %% coordinated with product and business teams to operationalize 250K
  %% leads in \salesforce from scraped web data

  \hangindent=1.0em ---~Oversaw technical decisions, engaged in
  mentorship, established best practices, coordinated with
  stakeholders, and led multiple major technical initiatives on a
  team of 5 developers

  ---~Built out an ETL management and machine learning platform
  using \python, \clojure, \hive, and \spark
}

\industry{2012\textemdash{}2014}%
{Technical Lead}%
{\href{http://www.terrastride.com/}{TerraStride, Inc.}}%
{Software developer in an agile startup environment creating the
  \href{http://www.huntstand.com}{huntstand.com} web
  application. Written using \python, \django, and \backbone; deployed
  to \skill{AWS}.  Responsible for curating full technology stack and
  coordinating with $5$ developers.}

\industry{2011\textemdash{}2013}%
{Project Manager}%
{Palmetto Computer Labs}%
{Assisted in planning the POSSCON conference. Managed the Open IT Lab
  and associated projects (Android Development). Provided software
  support for websites and managed projects.}

\industry{2011}%
{Contractor}%
{Elastic Vision Consulting}%
{Created a parser and generator for XML medical records formats (CCR
  and CCD) in Java using JDOM, JAXB, SAX, Xerces, and Hibernate
  (HSQLDB), on an Axis2+Jetty6 driven server.}

%% \industry{2005}%
%% {Intern --- Technical Writer}%
%% {JAARS, Inc.}%
%% {Created documentation and integrated context-sensitive online help
%%   system for speech and linguistic software written in C++ and Visual
%%   Basic.}

%% \industry{2001\textemdash{}2002}%
%% {Volunteer Software Developer}%
%% {JAARS, Inc.}%
%% {Spearheaded the conversion from VB4 to VB6 for the linguistic
%%   reference tool
%%   \href{http://www.sil.org/computing/ipahelp/ipaprvw2.htm}{IPA Help}.}

\end{longtable}

\pagebreak

\section{Research Experience}

\begin{longtable}{@{}p{2.4cm}|p{13.6cm}}

\experience{2011---2013}%
{Research Assistant funded by \textsc{AFOSR}}%
{Materials Volume Segmentation}%
{Developed segmentation methods for materials image
  volumes in \emph{Python+NumPy/SciPy} and \emph{MATLAB} at the
  \textsc{Computer Vision Lab} at \textsc{USC}. Managed the lab
  computer network and organized weekly lab meetings.  Created GUI
  interface using wxWidgets for assisted segmentation, and conducted
  large-scale evaluations on multiple datasets for metallic and
  biological materials.}

\experience{2010---2011}%
{Research Assistant funded by \textsc{DARPA}}%
{Video Event Recognition}%
{Explored segmentation methods for video event
  recognition. Attended P.I. meetings in San Diego (2010) and
  Colorado (2011). Developed algorithms in \emph{Scheme} to process
  a corpus of thousands of videos extracted into over 3 million
  frames using a high-performance computing cluster.}

\experience{2009---2010}%
{NEH Fellow at the \textsc{Center for Digital Humanities}}%
{Digital Collation}%
{Created a \textsc{digital collation} application to
  handle automatic differencing of sub-textual inconsistencies among
  multiple copies of \emph{The Faerie Queene} by \textsc{Edmund
    Spenser} in \emph{MATLAB} to process tens of thousands of book
  page images.}

\end{longtable}

\section{Teaching Experience}
\vspace{-1em}

\begin{longtable}{@{}p{2.4cm}|p{13.6cm}}

\experience{2008--2009}%
{GK-12 Fellow at \textsc{Crayton Middle School}}%
{8\textsuperscript{th} Grade Science}%
{Served in Crayton Middle School, coordinating with the classroom instructor to enhance the science curriculum and activities in an 8\textsuperscript{th} grade science classroom. Subsequently coordinated and taught at the \textsc{GK-12 Institute for Teachers}, presenting the activities developed and delivered in the classroom.}

\experience{2007--2008, 2011}%
{Graduate Teaching Assistant at \textsc{USC}}%
{Web Development}%
{Supervised CSCE~145 labs, covering software development with \textsc{Java}, and taught CSCE~102, covering \textsc{Javascript}, \textsc{HTML}, and \textsc{CSS}. Taught~CSCE~211 covering digital logic design.}

\experience{Spring 2007}%
{Instructor for \textsc{CSCE 204} at \textsc{USCL}}%
{Introductory Programming}%
{Hired as special faculty. Taught introductory Visual Basic for majors and non-majors. Selected textbooks, developed all course material, graded all assignments. Worked with Dr. Noni M. Bohonak}

\experience{Fall 2006}%
{Camp Instructor for \textsc{USCL Arts and Sciences Adventure Camp}}%
{5\textsuperscript{th}-8\textsuperscript{th} Grade Students}%
{Worked in collaboration with Dr. Dwayne Brown. One of two instructors teaching Math and Computer Science to grade school students.}

\experience{2003--2007}%
{Professional Tutor at \textsc{USCL Academic Success Center}}%
{High School and College Students}%
{Student and graduate tutor for college-level Mathematics, Computer Science, Physics, and English classes.}

\end{longtable}

\pagestyle{myheadings}
\markright{Jarrell Waggoner}


\let\originalbibitem\bibitem
\def\bibitem#1#2\par{%
  \noexpandarg
  \originalbibitem{#1}
  \StrSubstitute{#2}{Jarrell Waggoner}{\textbf{Jarrell Waggoner}}\par}

%\section{Publications}
\nocite{waggoner:15}
\nocite{zhou:14}
\nocite{waggoner:phd}
\nocite{waggoner:14}
\nocite{waggoner:13a}
%% \nocite{waggoner:13b}
\nocite{waggoner:13c}
\nocite{waggoner:11}
\nocite{wang:11}
\nocite{temlyakov:10}
\nocite{zhang:10}
\nocite{waggoner:12}
\nocite{barbu:12}
\nocite{barbu:12b}
\nocite{zhang:12}
\nocite{temlyakov:13}
\nocite{salvi:13a}
\nocite{salvi:13b}

\renewcommand\refname{Publications}
\bibliography{cv}
\bibliographystyle{plainyr-rev}

\section{Posters/Presentations}
\begin{enumerate}
\renewcommand{\labelenumi}{[P\arabic{enumi}] }
\item Rules Engines: Logic As Data Structure. \emph{Palmetto Open Source Software Conference}. Columbia, SC. April 14, 2015.
\item Python for Computer Vision. \emph{All Things Open}. Raleigh, SC. October 24, 2013.
\item Interactive Grain Image Segmentation Using Graph Cut Algorithms. \emph{USC Graduate Student Day}. Columbia, SC. April 12, 2013.
\item Extending Django.  \emph{Palmetto Open Source Software
    Conference}.  Columbia, SC.  March 28, 2013.
\item Computer Science: Research, Industry, and Entrepreneurship.
  \emph{Careers in Science Lecture Series}.  Lancaster, SC.  March 6,
  2013.
\item Interactive Grain Image Segmentation Using Graph Cut Algorithms.
  \emph{SPIE (Computational Imaging XI)}.  Burlingame, CA.  February
  6, 2013.
\item Homeomorphic Multi-Structure Propagation for Metallic Image
  Segmentation.  \emph{Gamecock Computing Research Symposium}.
  Columbia, SC.  October 5, 2012.
\item Android Application Development Workshop.  \emph{Appathon
    Contest}.  Columbia, SC.  November 17, 2012.
\item Open Source and Education. \emph{SC Municipal Technology
    Association (SCMTA) Conference}. Charleston, SC.  September 6,
  2012.
\item Open Source and Higher Education.  \emph{SC Technical College
    System (SCTCS) Conference}.  Columbia, SC.  September 25, 2012.
\item Introduction to Android Development.  \emph{Digital Humanities
    High Performance Computing (DHHPC) Workshop}.  Columbia, SC.
  August 8, 2012.
\item Combining Global Labeling and Local Relabeling for Metallic
  Image Segmentation.  \emph{SPIE (Computational Imaging X)}.
  Burlingame, CA.  January 23, 2012.
\item Open Source and Government.  \emph{SC Government Management
    Information Systems (SCGMIS) Software Developers Workshop}.
  Columbia, SC.  January 19, 2012.
\item Superpixel Contour Completion.  \emph{DARPA Mind's Eye PI
    Meeting}.  Denver, CO.  January 20, 2011.
\end{enumerate}

%% \section{Guest Lectures}
%% \begin{enumerate}
%% \renewcommand{\labelenumi}{[G\arabic{enumi}] }
%% %% \item \emph{Combining Global Labeling and Local Relabeling for Metallic Image Segmentation}. Graduate Student Day Competition, Second Place. April 8, 2011.
%% %% \item \emph{Image Registration for Digital Collation}. Graduate Student Day Competition, Honorable Mention. April 2, 2010.
%% \item \emph{Building Chrome Extensions}.  In CSCE 242.  Guest lecture for Dr. José M. Vidal.  November~30, 2012.
%% \item \emph{Modeling in Blender}.  In CSCE 552.  Guest lecture for Dr. Jijun Tang.  February~28, 2011.
%% \item \emph{Aspect-Oriented Programming}. In CSCE 531. Guest lecture for Dr. Marco Valtorta. March 19, 2008.
%% \item \emph{Math 241}. Vector Calculus. Guest lecture for Dr. Dwayne Brown. April~23---26, 2007.
%% \item \emph{Math 242}. Differential Equations. Guest lecture for Dr. Dwayne Brown. April~23---26, 2007.
%% \end{enumerate}

%\section{Travel}
%\begin{enumerate}
%\renewcommand{\labelenumi}{[T\arabic{enumi}] }
%\item \emph{Mind's Eye PI Meeting}. DARPA Project P.I.~meeting. Denver, CO. January 20---21, 2011.
%\item \emph{Tomography and its Applications to Materials Science and Non-Destructive Evaluation}. Organizd by M. De Graef, L. Drummy, J. Simmons, M. Comer, C. Bouman, and J. Knopp. Tech\^{}Edge, Dayton, Ohio. December 13---15, 2010.
%\item Visiting scholar. In collaboration with J. M. Siskind. Purdue University, West Lafayette, IN. December 6---22, 2010 \& January 5---16, 2011.
%\item \emph{Mind's Eye Kickoff Meeting}. DARPA Project P.I.~meeting. San Diego, CA. September 23---24, 2010.
%\end{enumerate}

\section{Honors/Awards}
\begin{center}
\begin{tabular*}{0.75\textwidth}{rll}
2012 & Gamecock Computing Research Symposium Poster Session,  First Place & \multirow{5}{*}{{\lighttext \textcolor{lightg}{\begin{turn}{-90}USC\end{turn}}}}\\
     & Graduate Student Day Presentation,  First Place \\
2011 & Graduate Student Day Presentation,  Second Place \\
2010 & Graduate Student Day Presentation,  Honorable Mention \\
2009 & Upsilon Pi Epsilon \\
% \multicolumn{3}{r}{}\\
% 2006 & Senior Computer Science Award & {\lighttext \textcolor{lightg}{Bryan College}}\\
\multicolumn{3}{r}{}\\
2004 & Clara P. Hammond Award & \multirow{3}{*}{{\lighttext \textcolor{lightg}{\begin{turn}{-90}USCL\end{turn}}}} \\
& Science and Mathematics Award \\
& Highest Academic Average Award \\
\end{tabular*}
\end{center}

%\section{Professional Societies}

\section{Classes Taught}
\vspace{-1em}
\begin{center}
%\begin{tabular*}{0.75\textwidth}{r @{\hspace{0.5em}\textcolor{lightg}{\symbol{"00BB}}\hspace{0.5em}} l @{\extracolsep{\fill}} l }
\begin{tabular*}{0.75\textwidth}{r @{\hspace{0.5em}\textcolor{lightg}{\symbol{"00BB}}\hspace{0.5em}} l l c }
%\multicolumn{3}{r}{University of South Carolina}\\
2012--2013 & Open Source 101 & Open Source Software & \multirow{3}{*}{{\lighttext \textcolor{lightg}{\begin{turn}{-90}IT-oLogy\end{turn}}}}  \\
2012--2013 & Version Control 101 & git, github \\
2012--2013 & Command Line 101 & Linux, BASH \\
\multicolumn{3}{r}{}\\
Fall 2011 & CSCE 211 & Digital Logic Design & \multirow{4}{*}{{\lighttext \textcolor{lightg}{\begin{turn}{-90}USC\end{turn}}}} \\
Summer II 2008 & CSCE 102 & HTML/CSS/JavaScript \\
Spring 2008 & CSCE 145 Lab & Java \\
Fall 2007 & CSCE 145 Lab & Java \\
\multicolumn{3}{r}{}\\
%\multicolumn{3}{r}{University of South Carolina at Lancaster}\\ \hline
Spring 2007 & CSCE 204 & Visual Basic & \multirow{2}{*}{{\lighttext \textcolor{lightg}{\begin{turn}{-90}USCL\end{turn}}}} \\
Spring 2007 & Math 241 \& Math 242 & Maple \\
\end{tabular*}
\end{center}

\section{Service}
\vspace{-1em}
\newcommand{\service}[2]{
  \textsc{#1} & #2\\
  %% \multicolumn{2}{c}{} \\
}
\begin{longtable}{r|p{10cm}}
  \service{Itern mentoring}{Groupon internship program, 2014}
  \service{Webmaster}{\href{http://cvl.cse.sc.edu/wvm2013/}{Winter Vision Meetings, 2013}}
  \service{Webmaster}{\href{http://cvl.cse.sc.edu/wacv2013/}{Workshop on the Applications of Computer Vision, 2013}}
  \service{Judge}{Discovery Day --- Undergraduate Research Presentations}
  \service{Reviewer}{Pattern Recognition Letters}
  \service{Reviewer}{IEEE Transactions on Pattern Analysis and Machine Intelligence}
  %% \service{Fellow}{NSF GK-12 Program}
  \service{Member}{Institute of Electrical and Electronics Engineers (IEEE)}
  \service{SysAdmin}{Computer Vision Lab}
\end{longtable}

%% \vspace{1em}

\section{Personal and Open Source Projects}
\newcommand{\proj}[3]{
  \textsc{#1} & #2\\
   &\href{http://www.#3}{#3}\\
   \multicolumn{2}{c}{} \\ [-1.5ex]
}

\newcommand{\projlh}[4]{
  \textsc{#1} & #2\\
   &\href{#3}{#4}\\
}

\begin{longtable}{@{}p{3cm}|p{13cm}}

  \proj{matsciseg}%
  {Framework for propagated 3D volume segmentation, used in my dissertation work.  Algorithms created in \python and \cpp and exposed as a web API using \django. Includes a web application that consumes the API created in \js, and \jquery.}%
  {github.com/malloc47/matsciseg}

  \proj{\href{http://nonpartisan.me}{nonpartisan.me}}%
{Google Chrome extension that filters social media websites for political keywords.  Available in the \href{https://chrome.google.com/webstore/detail/nonpartisanme/ninebcppidndhampaggnjbijpacoadgg}{Chrome Web Store}.  Featured in the \href{http://www.charlestoncitypaper.com/charleston/sick-of-politics-on-facebook-try-this-browser-tool/Content?oid=4153447}{Charleston City Paper}.}%
{github.com/malloc47/nonpartisan.me}

\proj{term-do}{An interactive terminal prompt that displays potential command completions as you type.  A hybrid of gnome-do and Emacs's ido-mode.  Works on many tested VT100 terminal types; built in~\skill{C++}.  Includes client/server architecture implemented with boost.interprocess and full-featured plugin system. Available in the \href{https://aur.archlinux.org/packages/term-do-git/}{Arch Linux AUR}.}{github.com/malloc47/term-do}

  \proj{Ratio Contour}{Maintainer and contributor for the Ratio Contour project, a salient object detection and segmentation method used for computer vision applications.  Developed in \skill{C} and \skill{MATLAB}.}{github.com/malloc47/ratio-contour}

  \proj{Digital Collation}{Research project to ``collate'' high-resolution documents by using image registration, accomplished using the SIFT feature detector and a thin plate spline warping technique, written in MATLAB.}{github.com/malloc47/digital-collation}

  % \proj{PMLDAP}{\skill{Linux} user management tool for Linux clusters.  Created as a simplified replacement for LDAP.  Capable of bootstrapping new systems, synchronizing users and configuration files, and running distributed commands.  Written in \skill{Bash}.}{github.com/malloc47/pmldap}

  % \proj{matscicut}{An energy minimization framework for segmenting 3D materials volumes. Prototype of dissertation work, created in C++ using OpenCV libraries, with assorted MATLAB helper utilities.}{github.com/malloc47/matscicut}

  % \proj{git-hq}{A remote management system for git, created in Python.}{github.com/malloc47/git-hq}

  %% \proj{Sina Weibo Mobile Client}{Created a \skill{J2ME}-based prototype mobile client for the popular Chinese \institution{Sina} microblogging service, similar to \institution{Twitter}.  Targeted at limited-functionality CLDC phones and uses a custom \skill{Java} wrapper for the \institution{Sina} API.  Employs symmetric-key encryption for personal data.}{bd.weibo.10086.cn/2012/downloads\_kjav}

  \proj{befunge.py}{Complete \href{https://en.wikipedia.org/wiki/Befunge}{Befunge} interpreter written in \python.  Implements the Befunge 93 specification, and is one of the closest Python equivalents to the \c reference implementation.}{github.com/malloc47/befunge.py}

\end{longtable}

\begin{minipage}{\linewidth}
\newcommand{\skills}[2]{
  \item #2 #1
}
\section{Skills \& Languages}
\begin{multicols}{4}
\raggedcolumns
\begin{itemize}
\renewcommand{\labelitemi}{}
\renewcommand{\skill}{\textnormal}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

\skills{\bash}{\threeskill}
\skills{\ccpp}{\threeskill}
\skills{\clojure}{\threeskill}
\skills{Emacs Lisp}{\twoskill}
\skills{\haskell}{\oneskill}
\skills{\java}{\threeskill}
\skills{\js}{\twoskill}
\skills{\LaTeX}{\twoskill}
\skills{\python}{\threeskill}
\skills{\scheme}{\threeskill}
\skills{\matlab}{\twoskill}

\skills{\django}{\twoskill}
\skills{\git}{\threeskill}
\skills{\numpy/\scipy}{\threeskill}
\skills{\opencv}{\threeskill}

\skills{GNU/\linux}{\threeskill}
\skills{\hadoop}{\threeskill}
\skills{\hive}{\oneskill}
\skills{\postgres}{\threeskill}
\skills{\spark}{\threeskill}

% graveyard

%% \skills{English}{\threeskill}
%% \skills{Blender}{\twoskill}
%% \skills{Sys. Admin.}{\threenotes}
%% \skills{Visual Basic}{\fivenotes}
%% \skills{Windows}{\fivenotes}
%% \skills{Wordpress}{\fournotes}
%% \skills{\html}{\threeskill}
%% \skills{Processing}{\fivenotes Image}
%% \skills{\jquery}{\twoskill}
%% \skills{LAMP Stack}{\fournotes}
%% \skills{LISP}{\onenote}
%% \skills{Learning}{\fournotes Machine}
%% \skills{Maple}{\twoskill}
%% \skills{MS Office}{\fivenotes}
%% \skills{Networking}{\threenotes}
%% \skills{\php}{\oneskill}

\end{itemize}
\end{multicols}
\begin{footnotesize}
  \oneskill Small-scale projects and/or assignments \hfill
  \twoskill Multiple projects and/or experience teaching \hfill
  \threeskill Large-scale and/or multi-group projects
\end{footnotesize}
\end{minipage}

\section{Activities}
teaching, programming, open source software, system administration,
data visualization, Linux,
\href{https://soundcloud.com/malloc47}{music composition}

\null\vfill
\footnotesize{
  Online:  \href{http://cv.malloc47.com}{cv.malloc47.com} \hfill
  Résumé: \href{http://resume.malloc47.com}{resume.malloc47.com} \hfill
  Source:  \href{https://github.com/malloc47/cv/tree/master}{github.com/malloc47/cv/}
}

%%\XeTeXpdffile ''cv.pdf'' page 1 scaled 800

\end{document}
