% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Brenda Baud} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document} 
\thispagestyle{empty} % this page does not have a header
\name{BRENDA BAUD}
\address{222 South Main Street\\
North Adams, MA 01247\\
(413) 555 - 8610}


\begin{resume}
\vspace{0.1in}
\moveleft.5\sectionwidth\centerline{Objective: Position as technical writer or editor.}  

\section{EDUCATION}
\vspace{0.1in} 
 
    Rensselaer Polytechnic Institute, Troy, NY, Ph.D., 
    Communications and Rhetoric, 1989 
 
    Trinity College, Hartford CT, M.A., English, 1979 
 
    Montclair State College, Upper Montclair, NJ, B.A., English, 
    1968. English Honor Society 
 
 
\section{SPECIAL SKILLS} 
\vspace{0.1in}
  {\bf Writing}
    \begin{itemize} % Use \item[] to prevent a bullet from appearing
      \item[] Academic papers, technical reports, functional documents, 
        newsletters, nonfiction articles. Published papers on 
        technical writing, research in organizational writing. 
        Wrote computer documentation, including CAD/CAM, PC and 
        interface material. Produced technical papers on history 
        of technology; revised tables of contents, reference 
        material. 
      \end{itemize}
{\bf Editing} 
       \begin{itemize}
        \item[] Taught editorial writing courses; trained in editing 
        techniques (Garrison Institute of Writing); edited 
        research proposals, promotional material, newsletters.
    \end{itemize}

  {\bf Training and Administration} 
        \begin{itemize}
        \item[] Taught technical writing, business writing, upper 
        division writing courses for engineering, computer 
        science, management students. Trained teachers in 
        graduate-level writing course. Led professional 
        development workshops in business writing to college 
        administrators. Supervised teaching assistants; 
        coordinated tutoring network for academic support 
        services. 
       \end{itemize}

   {\bf  Research and Consulting} 
        \begin{itemize}
        \item[]  Investigated use of word processors as primary writing 
        implements in organizational settings. Developed 
        usability instrument for assessing computer 
        documentation; researched use of icons in interfaces. 
        Consulted in use of field methods for organizational 
        analysis. Provided writing consultations for graduate 
        research projects. Training in statistical methods in 
        communications research, introductory course, RPI. 
        Training in field research techniques, SUNY. 
       \end{itemize} 

   {\bf Computer Experience} 
        \begin{itemize}
        \item[] Courses: Basic, Pascal. Types and Programs: IBM 
        Mainframe/3081D (MTS: Textform, SPSSX; IBM MINI/360 
        (GML/SCRIPT, CAD/CAM); IBM PC (Multimate, Wordperfect); 
        Apple II-Plus (Macwrite, Pagemaker). 
        \end{itemize}
 
\section{EMPLOYMENT} 
\vspace{0.1in} 
    {\bf Lecturer,} Department of Language, Literature and 
    Communication, Rensselaer Polytechnic Institute, Troy, NY 
    1986-1987 
 
    {\bf Teaching Assistant,} Department of Language, Literature and 
    Communication, Rensselaer Polytechnic Institute  1985-1986 
 
    {\bf Instructor and Lecturer,} Department of English and 
    Communications, North Adams State College, North Adams, MA 
    1985 - 1986 
 
    {\bf Workshop Leader,} North Adams State College, North Adams, MA \\
    "Composition for Teachers: A Writing Across the Disciplines 
    Approach." Graduate School of Education, 1986; \\
    ``Effective Writing for Executives.'' Professional Development 
    Program, 1985; ``Informative and Persuasive Business Writing.''
    Winter Study, 1983 
 
    {\bf Writing Consultant,} Graduate School of Education, North Adams 
    State College, North Adams, MA  1985 
 
    {\bf Research Assistant,} Chesterwood, Stockbridge, MA  Summer 1985 
 
    {\bf Instructor,} Learning Skills Center, North Adams State 
    College, North Adams, MA  1979 - 1985 
 
    {\bf Acting Program Coordinator for Academic Tutoring and 
    Advising,} Learning Skills Center, North Adams State College, 
    North Adams, MA  Spring 1985 
 
    {\bf English Teacher,} Easthampton High School, Easthampton, MA and 
    West Orange, NJ.  Chair, English Department evaluation; 
    member, Alternative Learning Program.  1968 - 1979 
 
 
\section{PROFESSIONAL AFFILIATIONS} 
\vspace{0.1in} 
    Society of Technical Communication \\
    Association of Business Communication \\
    Modern Language Association \\
    National Council of Teachers of English \\
    Conference on College Composition and Communication \\
    Society of Professional Writing Consultants 

\section{PUBLICATIONS} 
\vspace{0.1in}
``Playing to Win,'' {\it Hers, The New York Times Magazine, July 3, 1988} 

 
``Analyzing Corporate Communications Policies using Ethnographic 
Methods,'' {\it The Proceedings of the Conference on Corporate 
Communications}, Fairleigh Dickinson University, Madison, NJ, May 
1988. 
 
``Toward a Cognitive Theory of Visual Processing,'' {\it The Proceedings 
of the ITCC, Society of Technical Communication}, Philadelphia, 
PA, May 1988. 
 
``Organizational, Interpersonal and Technological Influences on 
Newspaper Writing, An Ethnographic Study,'' In review. 
 
``Combining Elegance and Readability: Walker Gibson's Tough, Sweet 
and Stuffy,'' {\it IEEE Transactions in Professional Communication}, 
December 1987. 
 
``Walker Gibson's Tough Sweet and Stuffy: A Workshop in Style for 
Engineers,'' {\it Linking Technology and Users: Conference Record of 
the IPCC}, October 1986. 
 
``That Damn Ram: Hydraulic Power at Chesterwood, 1908-1932,'' 
Unpublished paper for Chesterwood and the Society for Historic 
Preservation, 1984. 
 
``Sculpture Media,'' Unpublished paper for Chesterwood and the 
Society of Historical Preservation, 1984. 
 
{\it The Chesterwood Pedestal}, Volume 3, 1985, Newsletter of The 
Society of Historical Preservation, Chesterwood, Stockbridge, MA. 
 
\end{resume}
\end{document}






























