% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Susan R. Bumpershoot}
% \address used twice to have two lines of address
\address{1985  Storm Lane, Troy, NY 12180}
\address{(518) 273-0014 or (518) 272-6666}

 
\begin{resume}
 
\section{OBJECTIVE}       A position in the field of computers with special 
                interests in business applications programming, 
                information processing, and management systems. 
 
 
\section{EDUCATION} {\sl Bachelor of Science,} Interdisciplinary Science \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Rensselaer Polytechnic Institute, Troy, NY, 
                expected December 1990 \\
                Concentration: Computer Science \\
                Minor: Management 
 
 
\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} COBOL, IFPS, Focus, 
         Megacalc, Pascal, Modula2, C, APL, SNOBOL, 
                FORTRAN, LISP, SPIRES, BASIC, VSPC Autotab, 
                IBM 370 Assembler, Lotus 1-2-3. \\
                {\sl Operating Systems:} MTS, TSO, Unix.
 
\section{EXPERIENCE} {\sl Business Applications Programmer} \hfill Fall 1990 \\
                Allied-Signal Bendix Friction Materials Division, 
                Financial Planning Department, Latham, NY
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Developed four "user friendly" forecasting 
                    systems each of which produces 18 to 139 
                    individual reports. 
                \item   Developed or improved almost all IFPS 
                    programs used for financial reports. 
                \end{itemize}
 
                {\sl Research Programmer} \hfill            Summer 1990 \\
                Psychology Department, Rensselaer Polytechnic 
                Institute 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Performed computer aided statistical analysis 
                    of data. 
                 \end{itemize} 
                {\sl Assistant Manager} \hfill        Summers 1988-89 \\
                Thunder Restaurant, Canton, CT
                  \begin{itemize}
                   \item Recognized need for, developed, and wrote 
                    employee training manual. Performed various 
                    duties including cooking, employee training, 
                    ordering, and inventory control. 
                   \end{itemize} 
 
\section{COMMUNITY \\ SERVICE}  Organized and directed the 1988 and 1989 Grand 
                 Marshall Week \newline ``Basketball Marathon.'' A 24 hour 
                charity event to benefit the Troy Boys Club. Over 
                250 people participated each year. 

\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            Elected {\it House Manager}, Rho Phi Sorority \\
            Elected {\it Sports Chairman} \\
            Attended Krannet Leadership Conference \\
                Headed delegation to Rho Phi Congress \\
                Junior varsity basketball team \\
                Participant, seven intramural athletic teams 
 

\end{resume}
\end{document}







