%% rubric.tex --- Example of using CurVe.

%% Copyright (C) 2000, 2001, 2002, 2003, 2004, 2005 Didier Verna.

%% Author:        Didier Verna <didier@lrde.epita.fr>
%% Maintainer:    Didier Verna <didier@lrde.epita.fr>
%% Created:       Thu Dec 10 16:04:01 2000
%% Last Revision: Fri Feb  6 17:38:00 2004

%% This file is part of CurVe.

%% CurVe may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.1
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%% http://www.latex-project.org/lppl.txt
%% and version 1.1 or later is part of all distributions of LaTeX
%% version 1999/06/01 or later.

%% CurVe consists of the files listed in the file `README'.

\begin{rubric}{The Rubric's Title}
\subrubric{A Second Subrubric}
\entry*[A Key]
  This is an entry with a key. The key is displayed on the left, and you're
  reading the entry's contents. As you can see, this entry does not belong to
  a subrubric.
\subrubric{A First Subrubric}
\entry*[A Key]
  This entry belongs to the first subrubric. Before the subrubric,
  some space is added to separate it from the previous entry.
\entry*
  After the subrubric, some space is also added to separate it from the
  first entry. Note that this entry has no key. The entries contents are
  aligned together.
\entry*[Another Key]
  This is another entry with a new key.
\entry*
  This is another entry, but this one has no key. Note the text bullet
  which serves as a visual clue, especially when several entries share the
  same key.
\subrubric{A Second Subrubric}
\entry*[A Key]
  This entry belongs to the second subrubric.
\entry*
  This one also belongs to the second subrubric.
\entry*[Another Key]
  This is another entry with a new key.
\entry*
  This is another entry, but this one has no key.
  \subrubric{}
\entry*[A Key]
  If you want to separate some entries from the subrubric above,
  you can for instance make an empty subrubric.
\entry*
  You can include other rubrics below. Rubrics can even be split across
  pages. The titles will then be repeated.
\end{rubric}

%% rubric.tex ends here.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "cv"
%%% End:
